Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-22 main.tex
:pencil: Update model for multi-antenna AP

	\begin{section}{The Multi-Tag Case}
		% We then extend the algorithm to the $K$-tag case and characterize the achievable legacy rate-backscatter sum-rate region.

		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $h^{\mathrm{D}}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $h_k^{\mathrm{F}}$, the TG $k$-UE backward channel as $h_k^{\mathrm{B}}$, and the cascaded forward-backward channel of tag $k$ as $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$.
			% Let $h_k^{\mathrm{C}} \triangleq h_k^{\mathrm{B}} h_k^{\mathrm{F}}$ be the cascaded forward-backward channel of tag $k$.
			For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and let the coherence interval $T$ be much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and thus lower rates) than the primary system. As such, we assume all tags are perfectly synchronized and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

			Without loss of generality, we focus on the transmissions during the interval of one particular backscatter symbol. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
			% at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the primary symbol $s[n] \sim \mathcal{CN}(0,1)$ is assumed in standard CSCG distribution. On the other hand, let the backscatter symbol $c_k$ of tag $k$ employ $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$.
			Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times and assume the time difference of arrival from different paths are negligible\cite{Wu2019,Guo2019b}.}
			\begin{equation}
				y[n] = \sqrt{P} \left(h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k\right) s[n] + w[n],
			\end{equation}
			where $P$ is the average transmit power at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$. Also, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h^{\mathrm{E}}(\boldsymbol{c}) \triangleq h^{\mathrm{D}} + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} h_k^{\mathrm{C}} c_k.
			\end{equation}

			\begin{remark}
				The proposed symbiotic radio system is reminiscent of a Multiple Access Channel (MAC) where the AP and the tags transmit simultaneously to the user. It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first decode the primary message in the presence of backscatter uncertainty, then cancel its contribution and decode the backscatter messages. However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed multiplied in the backscattered signals. Therefore, the benefits of SIC might not outstand for symbiotic radio systems.
			\end{remark}
		\end{subsection}

>>>>

	\begin{section}{The Multi-Tag Case}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and thus lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

			Without loss of generality, we focus on the transmissions and detections during the interval of one particular backscatter symbol. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times and assume the time difference of arrival from different paths are negligible\cite{Wu2019,Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathbb{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

			\begin{remark}
				The proposed symbiotic radio system is reminiscent of a Multiple Access Channel (MAC) where the AP and the tags transmit simultaneously to the user. It inspired all existing papers [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty (requires non-coherent codes), then cancels its contribution and decodes the backscatter messages. However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) because the primary and secondary messages are indeed combined in the received signal by multiplication. Also, the computational complexity of SIC can be high since it requires $K$ re-encoding, precoding, and subtraction operations. Therefore, novel multi-stream detection techniques should be tailored for symbiotic radio systems.
			\end{remark}
		\end{subsection}
